### 2018-03-15 paper/sexSelectionSpacing-ver1.tex
Intro on changing sex ratios within spell and delete unneeded graphs

[

using conditional survival curves forces everybody to finish at the 
same month.
How many births are there?
We can show that using standard survival curves.
The flatter the curve the fewer births.

72 months = 6 years, plus the 9 months from the previous birth.
]

[Moved from estimation strategy]
In the absence of sex selection, I expect most parities to follow
a pattern, where there initially are relatively few births, 
followed by a substantial number of births over a 1 to 2 year period, and then
relatively few births thereafter.
As sex selection becomes more widely used the associated
longer spacing shows up by making the survival curve straighter,
indicating that some of the births that would originally have taken place
now take place later because of abortions.
The use of sex selection is clearly not the only factor that can change the shape of
the survival curves; factors such as the desired number of children and
use of contraceptives may also shape the shape.
To account for this it is best to compare survival curves for an individual
parity between women who are likely to use sex selection and women who are
not, for example because they already have one or more sons.

@@

@@

Figure \ref{fig:results_spell2_high_urban} 
shows the predicted probabilities of having a boy and standard survival curves
for the three periods for urban women with 8 or more years of education.%
\footnote{
The corresponding graphs for rural women and for women with no education are
shown in Figures \ref{fig:results_spell2_high_rural}, \ref{fig:results_spell2_low_urban},
and \ref{fig:results_spell2_low_rural}
}
Two main results stand out.
First, women whose first child was a boy do not appear to use sex selection during
the second spell.
The predicted percent boys is consistently close to the natural level in all three
panels (\ref{fig:results_spell2_high_urban}(d)-(f)).
Second, as prenatal sex determination became available there is more and more
evidence of sex selection affecting the sex ratio for women with a girl as their
first child.
In panel (a), which covers the period before sex selection became generally
available, there is no significant evidence of a sex ratio biased towards males.
Panel (b) shows a more male biased sex ratio but only a few months show
a statistically significant difference from the natural rate and the shallow 
slope of the survival curve indicates that relatively few births took place
during these months.
Panel (c), however, shows clear evidence of the effect of access to prenatal
sex determination with a male biased sex ratio for more of the two first years.%
\footnote{
Recall that month 0 is equivalent to 9 months after the birth
of the first child.
}

@@

\appendix
\section{Appendix}

% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
\renewcommand\thefigure{\thesection.\arabic{figure}}    
\setcounter{figure}{0}
\renewcommand\thetable{\thesection.\arabic{table}}    
\setcounter{table}{0}

@@

\subsection{Additional Duration Results}

@@

\subsection{Second Spell}

% SPELL 2 - URBAN - LOW
\begin{figure}[h]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=1,596)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=2,232)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=952)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=1,754)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=2,411)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=930)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with no education by month beginning 9 months after prior birth. 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_low_urban}
\end{figure}

% SPELL 2 - rural - LOW
\begin{figure}
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=8,426)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=11,481)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=3,686)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=9,395)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=12,127)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=3,860)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural 
women with no education by month beginning 9 months after prior birth. 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_low_rural}
\end{figure}

% \begin{figure}[htpb]
% \centering
% \caption*{First child a girl}
% \setcounter{subfigure}{-2}
% \subfloat[1972--1984 (N=2,689)]{
%     \begin{minipage}{0.31\textwidth}
%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
%         \captionsetup[subfigure]{labelformat=parens}
%     \end{minipage}
% } 
% \setcounter{subfigure}{-1}
% \subfloat[1985--1994 (N=4,869)]{
%     \begin{minipage}{0.31\textwidth}
%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
%         \captionsetup[subfigure]{labelformat=parens}
%     \end{minipage}
% }
% \setcounter{subfigure}{0}
% \subfloat[1995--2006 (N=3,774)]{
%     \begin{minipage}{0.31\textwidth}
%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
%         \captionsetup[subfigure]{labelformat=parens}
%     \end{minipage}
% }
% \caption*{First child a boy}
% \setcounter{subfigure}{1}
% \subfloat[1972--1984 (N=2,806)]{
%     \begin{minipage}{0.31\textwidth}
%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
%         \captionsetup[subfigure]{labelformat=parens}
%     \end{minipage}
% } 
% \setcounter{subfigure}{2}
% \subfloat[1985--1994 (N=5,246)]{
%     \begin{minipage}{0.31\textwidth}
%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
%         \captionsetup[subfigure]{labelformat=parens}
%     \end{minipage}
% }
% \setcounter{subfigure}{3}
% \subfloat[1995--2006 (N=3,969)]{
%     \begin{minipage}{0.31\textwidth}
%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
%         \captionsetup[subfigure]{labelformat=parens}
%     \end{minipage}
% }
% \caption{Predicted probability of having a boy and probability of
% no birth yet from nine months after first birth for urban 
% women with 8 or more years of education by month beginning 9 months after prior birth. 
% Predictions based on age 22 at first birth.
% Left column shows results prior to sex selection available, middle column before
% sex selection illegal and right column after sex selection illegal.
% N indicates the number of women in the relevant group in the underlying samples.
% }
% \label{fig:results_spell2_high_urban}
% \end{figure}

\begin{figure}[htpb]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=1,305)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=3,105)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,823)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=1,404)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=3,381)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,044)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural
women with 8 or more years of education by month beginning 9 months after prior birth. 
Predictions based on age 22 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_high_rural}
\end{figure}

\subsection{Third Spell}

% low education

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=493)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_gg_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_gg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=996)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_gg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_gg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=475)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_gg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_gg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=1,083)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=2,141)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=950)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by month beginning 9 months after prior birth. 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_low_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=569)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bb_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,124)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bb_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=426)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bb_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_spell3_low_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by month beginning 9 months after prior birth. 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=2,599)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_gg_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_gg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=5,062)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_gg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_gg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,879)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_gg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_gg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=5,382)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=10,473)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,779)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by month beginning 9 months after prior birth. 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_low_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=3,070)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bb_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=5,339)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bb_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=1,846)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bb_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by month beginning 9 months after prior birth. 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_spell3_low_rural}
\end{figure}

>>>>

The results so far show that as sex ratios have become more
male-biased the spacing when a woman has only girls have become 
longer relative to other sex compositions, presumably because
of increased use of sex selection rather than because of a
change in the degree of son preference.
Neither the median spacing or the conditional survival curves
can, however, provide us with information on how the use of
sex selection vary \emph{within} a spell.
Furthermore, using conditional survival curves forces everybody 
to finish the spell in the same month and does not provide
any information about how many births there are.
We can, however, learn something about both changes in 
sex selection within a spell and the likelihood of exiting
with a birth using standard  survival curves.

In the absence of sex selection, I expect most parities to follow
a pattern, where there initially are relatively few births, 
followed by a substantial number of births over a 1 to 2 year period, and then
relatively few births thereafter.
As sex selection becomes more widely used the associated
longer spacing shows up by making the survival curve straighter,
indicating that some of the births that would originally have taken place
now take place later because of abortions.
The use of sex selection is clearly not the only factor that can change the shape of
the survival curves; factors such as the desired number of children and
use of contraceptives may also shape the shape.
To account for this it is best to compare survival curves for an individual
parity between women who are likely to use sex selection and women who are
not, for example because they already have achieved their desired 
number of sons.

The flatter the curve the fewer births.

@@

[conditional survival curves]
72 months = 6 years, plus the 9 months from the previous birth.

@@

@@

\appendix
\section{Online Appendix}

% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
\renewcommand\thefigure{\thesection.\arabic{figure}}    
\renewcommand\thetable{\thesection.\arabic{table}}

\setcounter{figure}{0}
\setcounter{table}{0}

@@

\section{Additional Duration Results}

\setcounter{figure}{0}
\setcounter{table}{0}

@@
